Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-11 paper/ms.tex
Move discussions of actions up in intro

These measurements of the galactocentric coordinate system rely on the
assumption of an axisymmetric Milky Way. Under this assumption, these
estimates would provide the correct parameters for the Galactocentric
coordinate system up to measurement error. However, the Milky Way is not
axisymmetric in detail. Spiral arms, bar(s), and infalling satellite galaxies
such as Sagittarius and the Large Magellanic Cloud all induce
non-axisymmetries.

@@

Since an azimuthal-dependent midplane is effectively a departure from a
perfectly axisymmetric potential, we consider the effect that an erroneous
midplane has on the conservations of actions. The actions of an orbit are
typically computed in a cylindrical coordinate system as,
\beq\label{eq:actions}
J_i \equiv
\frac{1}{2\pi} \oint_{\text{orbit}}p_i\,\text{d}x_i\text{,}
\eeq
where $i=R,z,\phi$. Note that $J_{\phi} \equiv L_z$. In a slowly-evolving
axisymmetric potential, the actions of stars' orbits are conserved quantities
\citep{2008gady.book.....B,2014RvMP...86....1S}. The non-axisymmetries of a
more realistic potential induce time evolution in the {\em measured} actions
--- the true orbital invariants (if they exist) are invariant by definition.
Through simple tests, we will see that even in a truly axisymmetric potential,
if the wrong coordinate system is assumed then there will be additional time
evolution in the measured actions.

>>>>

Once a Galactocentric coordinate system has been established and a 6D phase
space measurement of a star has been made, it is desirable to convert this
measurement into action space. Actions are quantities which describe the orbit
of a star and are conserved quantities under some assumptions which we
describe next. They are the typical integral of the Hamiltonian in cylindrical
coordinates and are given by,
\beq\label{eq:actions}
J_i \equiv
\frac{1}{2\pi} \oint_{\text{orbit}}p_i\,\text{d}x_i\text{,}
\eeq
where $i=R,z,\phi$.\footnote{We typically write $J_r$ instead of $J_R$ for
aesthetic reasons.} Note that $J_{\phi} \equiv L_z$. In a slowly-evolving
axisymmetric potential, the actions of stars' orbits are conserved quantities
\citep{2008gady.book.....B,2014RvMP...86....1S}. The non-axisymmetries of a
more realistic potential induce time evolution in the {\em measured} actions
--- the true orbital invariants (if they exist) are invariant by definition.

@@
